## The goal is to find companies that uses active pricing.

Find a frequency of changing prices for each supplier. So for each supplier, we calc changes_count. This number is a number of prices for each acriss_code of supplier. So if the prices appear the same for the same acriss_code during time (different requests), this number will be small. If price changes for each ACRISS code, then supplier changes prices often.

```{r}
library(dplyr)

data <- read.csv("sample.csv")

# cleaning columns
d <- data[, c("acriss_code", "price_per_day", "supplier_name")]

calc_coeficients <- function(data) {
  
  d <- data %>%
    # for each supplier name
    group_by(supplier_name) %>%
    # for each accriss code within supplier
    group_by(acriss_code, add=TRUE) %>%
    # see how often prices were changed
    mutate(changes_count=length(table(price_per_day))) %>%
    ungroup() %>%
    # how often supplier was requested
    add_count(supplier_name) %>%
    group_by(supplier_name) %>%
    # sum all prices changes and divide by count of requests
    summarize(total=sum(changes_count)/mean(n)) # divide by total number of rows?
  
  return (d[order(d$total, decreasing = T), ] )
}
changes <- calc_coeficients(data)
```

### Let's test it. SUP2 didn't change prices for A2 cars. So it should have smaller coeficient.

```{r}
test_data <- data.frame(
  acriss_code=c("A1", "A2", "A2", "A2", "A1", "A2", "A1", "A2", "A1", "A1"),
  supplier_name=c("SUP1", "SUP2", "SUP2", "SUP2", "SUP1", "SUP2", "SUP1", "SUP2", "SUP2", "SUP2"),
  price_per_day=c(12, 22, 22, 22, 13, 14, 15, 22, 12, 13)
  )
print(test_data[order(test_data$supplier_name),])
```
So, SUP1 changed price frequently, while SUP2 changed price only once for A1 ACRISS code and once for A2. SO SUP2 don't use active pricing.

```{r}
test_res <- calc_coeficients(test_data)
print(test_res)
```
As result, SUP1 have higher coefficient. How it can be used? Say, this statistic can be updated every day/week/month to build target price using coeficients for supplier.
