---
title: "present"
author: "Girogi Sheklashvili"
date: "January 2, 2018"
output: pdf_document
---
In this file Im trying to repeate clustering method which is already sued by ratechain, In order to compare it with our clustering
```{r}
library(dplyr)
library(stringr)
#install.packages("factoextra")
library("factoextra")
```

```{r}
original <- read.csv("C:/Users/giusha9/Desktop/sample.csv")
head(original,2)
```
```{r}
original<-dplyr::filter(original, currency=="EUR")
original<-as.data.frame(original)
```
```{r}
original<-original[, !(colnames(original) %in% c("broker_location_code","rc_location_code","excess_included", "source","broker","source_country", "supplier_name","currency"))]

```

function for clustering only with acriss code and gearbox(result 3 clusters)
```{r}
acriss_func <- function(x, y) {
  acriss_x <- unlist(str_split(x$acriss_code, ""))[1]
  acriss_y <- unlist(str_split(y$acriss_code, ""))[1]
  acriss_diff <- ifelse(acriss_x == acriss_y, 0, 1)
  t_diff <- abs(x$transmission - y$transmission)
  return (acriss_diff+t_diff)
}

```

```{r}
data<-original%>%na.omit()%>%mutate(transmission = ifelse(transmission == "manual", 0, 1))

```
#distance matrix for rows(not using)
#```{r}
#
#dist_res <- proxy::dist(original[1:10,], method = acriss_func)
#dist_res
#```
```{r}
data<-data[ , !(colnames(data) %in% c("X","id","request_date","pickup_date","pickup_time","return_time","rental_days","destination_country","car_class_name","model_name","total_price","price_per_day"))]
data$acriss_code<-substring(data$acriss_code,1,1)

```
exporting data with only acriss code first letter and gearbox type
```{r}
write.csv(data,"C:/Users/giusha9/Desktop/data.csv")
```
read it again without header
```{r}
withoutHeader <- read.csv("C:/Users/giusha9/Desktop/data.csv",header = FALSE)
```
remove first column and row(first column is acriss code first letter, second is gearbox type)
```{r}
withoutHeader<-withoutHeader[-1, -1]
```

```{r}
matrix<-data.matrix(withoutHeader, rownames.force = NA)
```
```{r}
#matrix<-scale(matrix)
```


counting unique rows and running kmeans
```{r}
km.res<-kmeans(matrix,5,nstart = 25)
```

visualisation of clusters
```{r}
fviz_cluster(list(data = matrix, cluster = km.res$cluster),
             frame.type = "norm", geom = "point", stand = FALSE)
```



```{r}
original<-original%>%na.omit()%>%mutate(transmission = ifelse(transmission == "manual", 0, 1))
out <- cbind(original, clusterNum = km.res$cluster)
#group by cluster and find out top 5 best price
# top 10 cheapest average
tp <- out %>%
  group_by(clusterNum) %>%
  summarise(top10avg_price = mean(head(sort(price_per_day, decreasing = F ), 10)))

# percentile
tp_percentile <- out %>%
  group_by(clusterNum) %>%
  summarize(target_price_percentile = quantile(sort(price_per_day, decreasing=F), probs=0.95))

# 
tp_top5percent <- out %>%
  group_by(clusterNum) %>%
  summarize(target_price_top5 = mean(head(sort(price_per_day, decreasing = F), ceiling(n() * 0.05))))

tp
tp_percentile
tp_top5percent
```
