Let's find target prices. This is cheapest top 10 average and top 5 percentile.

```{r}
library(dplyr)

# read data
data <- read.csv("sample.csv") # 1 000 000 rows
# filter data
d <- data %>%
  select(model_name, acriss_code, car_class_name, transmission, price_per_day, currency) %>%
  na.omit() %>%
  filter(currency == "EUR") %>%
  mutate(transmission = ifelse(transmission == "manual", 0, 1))
```
Not let's edit model names to assign acriss codes

```{r}
# function to do that
get_model <- function (name) {
  # find index of ' or similar'
  i <- str_locate(name, " or similar")
  # remove 'group - x ' if in name
  if (grepl("^group ", name)) {
    car <- str_sub(name, 11)
  }
  # cut this 'or similar'
  car <- str_sub(name, 1, i - 1)[1]
  if(is.na(car)) {
    # sometimes happen
    car = tolower(name)
  } else {
    # but still need to be lower cased
    car = tolower(car)
  }
  return (car)
}
d$model_name <- sapply(d$model_name, get_model)
```
Now we try to assing 'correct' ACRISS codes just by getting it from mode of acriss_code for each model_name
```{r}
temp <- d %>%
  group_by(model_name) %>%
  mutate(acriss_code = names(which.max(table(acriss_code))))
```
Now we need to get rid of "anomalies" from "price_per_day". Some rows have values like 25 000 euro +. Per day. Really? For the same cars which have 90-100 euro price?
```{r}
#before
temp %>%
  filter(acriss_code %in% head(levels(as.factor(temp$acriss_code)), 20)) %>%
  ggplot(aes(x=acriss_code, y=price_per_day, colour=acriss_code)) + geom_point()
```
Do you see this scale? We want to cut these anomalies.
```{r}
# plot again
temp <- temp %>%
  group_by(acriss_code) %>%
  filter(price_per_day < quantile(price_per_day, c(.9)))

temp %>%
  filter(acriss_code %in% head(levels(as.factor(temp$acriss_code)), 20)) %>%
  ggplot(aes(x=acriss_code, y=price_per_day, colour=acriss_code)) + geom_point()
```
Much better. Now we can find target prices for each ACRISS code
```{r}
# top 10 cheapest average
tp <- temp %>%
  group_by(acriss_code) %>%
  summarise(top10avg_price = mean(head(sort(price_per_day, decreasing = F ), 10)))

# percentile
tp_percentile <- temp %>%
  group_by(acriss_code) %>%
  summarize(target_price = quantile(sort(price_per_day, decreasing=F), probs=0.95))

# 
tp_top5percent <- temp %>%
  group_by(acriss_code) %>%
  summarize(target_price = mean(head(sort(price_per_day, decreasing = F), ceiling(n() * 0.05))))

tp$top5_percentile <- tp_percentile$target_price
tp$top5_percent <- tp_top5percent$target_price
```
So for each ACRISS code we have target price - price, that one should set for his car to be in the cheapest top 5%, top 10 or in 5 percentile.

